Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-05-04 ms.Rmd
minor header change

  # Get model stats for ppaer
       coefAIC_court <- fixef(ConspicCourtshipAC)[3]
         CI_AC_court <- data.frame(confint(ConspicCourtshipAC))
    courship_anovaAC <- anova(ConspicCourtshipAC)

>>>>

  # Get model stats for paper
       coefAIC_court <- fixef(ConspicCourtshipAC)[3]
         CI_AC_court <- data.frame(confint(ConspicCourtshipAC))
    courship_anovaAC <- anova(ConspicCourtshipAC)
